A Framework for Coping with API Evolution in a Software Ecosystem Setting

### 2015-03-24 ibp/ibp.tex
Made changes to Summary and state of the art. Added references in the bib to the websites that were also missing

Apiary is a popular online API design service. Apiary focuses on a collaborative approach to creating APIs, the tool offers the ability to work with between 5 and 50 contributors on a single project. The unique part of this tool is that it provides a ``mock" API by which customers, developers or anyone with access can work with. This stage allows quick prototyping and testing of an API before any real coding has taken place. The tool, while useful, doesn't aim to solve the problem of handling changes to APIs but is instead a good platform to quickly prototype ideas.

Mashery provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:

@@

\subsection{Impact on Society}
If companies begin developing their APIs to fit the needs of ecosystems, it would not only have a great impact on these specific isolated environments; it would develop the whole software engineering industry. Therefore, the impact on society is potentially huge. Given that software is used by everyone, daily, improving software overall could improve peoples quality of life.

@@

>>>>

Apiary \cite{Apiary} is a popular online API design service. Apiary focuses on a collaborative approach to creating APIs, the tool offers the ability to work with between 5 and 50 contributors on a single project. The unique part of this tool is that it provides a ``mock" API by which customers, developers or anyone with access can work with. This stage allows quick prototyping and testing of an API before any real coding has taken place. The tool, while useful, doesn't aim to solve the problem of handling changes to APIs but is instead a good platform to quickly prototype ideas.

Mashery \cite{Mashery} provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:

@@

More importantly, the companies themselves will likely benefit from such a framework. Potentially, the framework could allow companies to develop APIs, and therefore software, quickly and more efficiently thus increasing their development speed. Furthermore, the framework could help companies make changes to existing APIs to have fewer side effects within their ecosystems, for example, it could allow companies to communicate more easily with their users when making changes to the APIs that they are using. This could mean that companies could make changes more frequently with less side effects.

\subsection{Impact on Society}
Companies are not the only entity that could benefit from the this framework. If companies begin developing their APIs to fit the needs of ecosystems, it would not only have a great impact on these specific isolated environments; it would develop the whole software engineering industry. Therefore, the impact on society is potentially huge. Given that software is used by everyone, daily, improving software overall could improve peoples quality of life.

@@

The software engineering and management programme has helped us immensely with our thesis. Specifically, Technical Analysis and design and the Software Architecture courses have provided us with a good background for designing systems. Coupling this with programming and the design and development of embedded systems courses means that we have all the skills we require to complete our thesis. It also goes without saying that all the courses in the program will be invaluable when it comes to future work. Be it studying for a masters degree, continuing the thesis study or starting down our desired career path, our studies in this program have equipped us well for the future.
